Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/main.tex
Added abstract

\begin{abstract}
Put abstract here
\end{abstract}

>>>>

\begin{abstract}
  In this work we investigate the behavior of stable marine boundary
  layers located near the coast of the Northeastern United States.
  Using the ExaWind LES codes, three stable atmospheric conditions
  were chosen to match the Cape Wind measurements of Archer \emph{et
    al} with wind speeds of 5 m/s, 10 m/s, and 15 m/s.  The behavior
  of the stable boundary layers, including mean flow quantities and
  turbulent statistics, are examined and compared to previous
  computations of the neutral and unstable offshore boundary layer at
  the same location.  This study also examines the domain and mesh
  requirements necessary to capture the turbulent scales for the
  stable offshore boundary layers.  Finally, we compare solutions
  computed using both Nalu-Wind and AMR-Wind solvers, and report on
  their relative accuracy and performance in this study.

\end{abstract}
